\documentclass[9pt,a4paper]{article}

\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{url}
\usepackage{amsmath}
\usepackage[table,x11names]{xcolor}



\begin{document}

Fechas importantes $2^{do}$ cuatrimestre 2019:

\begin{itemize}
\item Exámen:
\begin{itemize}
\item Primer parcial - 17/10
\item Primer recuperatorio - 07/11
\item Segundo recuperatorio - 12/12
\end{itemize}
\item Trabajos Prácticos:
\begin{itemize}
\item Presentación TP0 - 22/08
\item Entrega TP0 - 
\item Presentación TP1 - 05/09
\item Entrega TP1 - 
\item Presentación TP2 - 26/09
\item Entrega TP2 - 
\item Presentación TP3 - 31/10
\item Entrega TP3 - 

\end{itemize}

\end{itemize}

\begin{tabular}{ |l | l | l | l |}
\hline
Semana & Temas			& Lecturas     & Ejercicios						\\
\hline
01 - 22/08	& Rég. cursada, Tools, Amdahl, TP0 		& ch.1 \cite{caaqa}	&	1.1 1.2 1.3		\\
\hline
02 - 29/08	& Ec. de desempeño, ABI, MIPS & ch.1 \cite{caaqa}    &	\\
\hline
03 - 05/09	& ISA, Ejs ABI, TP1					&		ch.2 \cite{caaqa}	&			\\
\hline
04 - 12/09	& Assembly, ABI 	& 	 &	\\
\hline
05 - 19/09	& Memoria cache	& 	ch.5 \cite{caaqa}	&	\\
\hline
06 - 26/09	& Memoria cache, TP2	& 		&		\\
\hline
07 - 03/10	& Memoria virtual	& 		ch.5 \cite{caaqa} Sec. 3 y 4 \cite{wepskam}&	 \\
\hline
08 - 10/10	& Memoria virtual	&	\cite{wepskam} ch.5 \cite{caaqa} \cite{vmp1} \cite{vmp2} &	 \\
\hline
\rowcolor{green} 09 - 17/10	& Exámen parcial	& 	&	 \\
\hline
10 - 24/10	& Datapath, resolución ex. parcial	&		&							\\
\hline
 11 - 31/10	& Pipeline, Hazards, TP3	& 	&								\\
\hline
\rowcolor{green}12 - 07/11	& $1^{er}$ recup.			& 	 & \\
\hline
13 - 14/11 & Predictores salto, pipeline FP, desempeño			& 	&	\\
\hline
 14 - 21/11 & Presentaciones TP	&		&							\\
\hline
 15 - 28/11	& Presentaciones TP			&	&								\\
\hline
16 - 05/12 & Presentaciones TP 	&			& \\
\hline
\rowcolor{green} 17 - 12/12 & $2^{do}$ recup.			&		& \\
\hline

\end{tabular}

\renewcommand\refname{Lecturas}

\begin{thebibliography}{9}

    \bibitem{caaqa}
    David Patterson, John Hennessy, \textit{Computer Architecture a Quantitative Approach}, Elsevier, 3rd edition. ISBN: 1-55860-596-7. May 2002.  
  
    \bibitem{coadhsi}

    David Patterson, John Hennessy, \textit{Computer Organization and Design, the Hardware/Software Interface},  Elsevier, 3rd edition. ISBN: 1-55860-604-1. Aug. 2004. 
    
    \bibitem{vmp1}

    B.L. Jacob and T.N. Mudge, \textit{Virtual Memory: Issues of Implementation}, Computer, Vol. 31, No. 6, June 1998, pp. 33-43.

    \bibitem{vmp2}

    B.L. Jacob and T.N. Mudge, \textit{Virtual Memory in Contemporary Microprocessors}, IEEE Micro, Aug. 1998.
    
    \bibitem{mafstocm}

    Jean-Loup Baer, \textit{Microprocessor Architecture. From Simple Pipelines to Chip Multiprocessors}, Cambridge University Press. ISBN-13 978-0-521-76992-1. 2010

    \bibitem{wepskam}
    
    Ulrich Dreper, \textit {What every programmer should know about memory}

    \bibitem{mcch}
    
    Rajeev Balasubramonian and Norman P. Jouppi and Naveen Muralimanohar, \textit{Multi-Core Cache Hierarchies}, Morgan and Claypool Publishers, 2011.
    
    \bibitem{abi}
    
    System V Application Binary Interface, MIPS RISC Processor, 3rd Edition, The Santa Cruz Operation, February 1996 (http://www.sco.com/developers/devspecs/mipsabi.pdf).
\end{thebibliography}

\end{document}
